---
title: 'Homework #1 - Tamires Amorim'
author: "Tamires Amorim, Yamei li and Meirou Guan"
date: "9/11/2020"
output:
  html_document: default
  word_document: default
---

```{r}
load("workspace.RData")
```

Questions:

3. Can you get the dice to roll a 6 more or less than would be expected? How would you know - what is “more often”?

I rolled the dice 20 times and obtained for Die 1 (3, 6, 1, 2, 1, 3, 1, 3, 4, 6, 1, 1, 2, 6, 2, 5 , 2, 1, 5), and Die 2 (4, 3, 1, 3, 1, 5, 6, 2, 2, 4, 5, 3, 6, 1, 2, 6, 1, 6,3).The first die had "6" three times, and the second one four times. From my perspective, it was more often than I expected, because when I compared with other members of my group I was the only person that obtained more "6" as outcomes. Additionally, because the size of the sample was small it seems that obtaining a 6 at least 3 times was higher than what probability predicts.    

3. Can you write some code in R that will simulate a fair roll?

```{r}
roll_die = function(n) sample(1:6, n, rep = T)
```
```{r}
roll_die(20)
```

```{r}
roll_die = function(n) sample(1:6, n, rep = T,prob = c(rep(1/7, 5), 2/7))
```
```{r}
roll_die(20)
```

The first function is a simulation of a fair roll, where we rolled the die 20 times and the number 6 appeared three times. 
On the second function we manipulate the numbers to create the event "6" more often than on a fair roll. 
In the real world a die or a pair of dice, can be manipulated by drilling, sanding or heating to weight one side of the dice, this is the only way to increase the chances of obtaining the same number more than expected. Otherwise, since the events are independent within a sample the probability of a 6 to come will always be 1/6, no matter the amount of rolls. 


4. Practice R Basics for lecture 1.

```{r}
#glimpse(acs2017_ny) try this later
acs2017_ny[1:10,1:7]
```

```{r}
attach(acs2017_ny)
```


```{r}
summary(acs2017_ny)
```

4. Tell me something else interesting, that you learned from the data, for example about educational attainments in different neighborhoods in the city. Are there surprises for you?

It was interesting to observe on the data that an average of 0.3615 of people have been educated in New York City, however, educational attainments in different neighborhoods in the New York city is different. For example, in Bronx, the mean is 0.0538, which is much lower than the average for New York as a whole, serving as information to prove the the low level of education in the borough. In contrast, Manhattan has a mean of 0.04981, Staten Island 0.02084, Brooklyn, the mean is 0.126 and In Queens, the mean is 0.1111. 


```{r}
print(NN_obs <- length(AGE))
```


```{r}
summary(AGE[female == 1])
```


```{r}
summary(AGE[!female])
```


```{r}
# here i want to find average ages of men and women
mean(AGE[female == 1])
```

```{r}
sd(AGE[female == 1])
```

```{r}
mean(AGE[!female])
```

```{r}
sd(AGE[!female])
```
```{r include=FALSE}
eval (TRUE)
```


5. Differences in means can be complicated. Find the mean return on SP500 index (choose a time period). What is the mean return on days when the previous day’s return was positive? When the previous 2 days were positive? Negative? Now read about “hot hands fallacy” and tell if you think that helps investment strategy. (You might start with this tweet, and read the papers referenced.)

It was collected data from from 08.06.2020-09.10.2020 to analyze the SP500 index returns. The mean of the daily returns is 0.000992144 (calculated in Excel) as follow:

| Date          | Open    | High    | Low     | Close   | daily return | 
| Sept. 10, 2020 | 3412.56 | 3425.55 | 3329.25 | 3339.19 | 0.023678 | 
| Sept. 9, 2020 | 3369.82 | 3424.77 | 3366.84 | 3398.96 | 0.017584791 | 
| Sept. 8, 2020 | 3371.88 | 3379.97 | 3329.27 | 3331.84 | -0.020145025 | 
| Sept. 4, 2020 | 3453.6 | 3479.15 | 3349.63 | 3426.96 | 0.027756379 | 
| Sept. 3, 2020 | 3564.74 | 3564.85 | 3427.41 | 3455.06 | 0.008132999 | 
| Sept. 2, 2020 | 3543.76 | 3588.11 | 3535.23 | 3580.84 | 0.035125836 | 
| Sept. 1, 2020 | 3507.44 | 3528.03 | 3494.6 | 3526.65 | -0.015365857 | 
| Aug. 31, 2020 | 3509.73 | 3514.77 | 3493.25 | 3500.31 | -0.007525048 | 
| Aug. 28, 2020 | 3494.69 | 3509.23 | 3484.32 | 3508.01 | 0.002194977 | 
| Aug. 27, 2020 | 3485.14 | 3501.38 | 3468.35 | 3484.55 | -0.006732577 | 
| Aug. 26, 2020 | 3449.97 | 3481.07 | 3444.15 | 3478.73 | -0.001673024 | 
| Aug. 25, 2020 | 3435.95 | 3444.21 | 3425.84 | 3443.62 | -0.010195666 | 
| Aug. 24, 2020 | 3418.09 | 3432.09 | 3413.13 | 3431.28 | -0.003596326 | 
| Aug. 21, 2020 | 3386.01 | 3399.96 | 3379.31 | 3397.16 | -0.010043684 | 
| Aug. 20, 2020 | 3360.48 | 3390.8 | 3354.69 | 3385.51 | -0.003441136 | 
| Aug. 19, 2020 | 3392.51 | 3399.54 | 3369.66 | 3374.85 | -0.003158659 | 
| Aug. 18, 2020 | 3387.04 | 3395.06 | 3370.15 | 3389.78 | 0.004404416 | 
| Aug. 17, 2020 | 3380.86 | 3387.59 | 3379.22 | 3381.99 | -0.002303378 | 
| Aug. 14, 2020 | 3368.66 | 3378.51 | 3361.64 | 3372.85 | -0.002709874 | 
| Aug. 13, 2020 | 3372.95 | 3387.24 | 3363.35 | 3373.43 | 0.000171932 | 
| Aug. 12, 2020 | 3355.46 | 3387.89 | 3355.46 | 3380.35 | 0.002047125 | 
| Aug. 11, 2020 | 3370.34 | 3381.01 | 3326.44 | 3333.69 | -0.013996502 | 
| Aug. 10, 2020 | 3356.04 | 3363.29 | 3335.44 | 3360.47 | 0.007969123 | 
| Aug. 7, 2020 | 3340.05 | 3352.54 | 3328.72 | 3351.28 | -0.002742236 | 
| Aug. 6, 2020 | 3323.17 | 3351.03 | 3318.14 | 3349.16 | -0.000632995 |

	

The mean return on S&P500 index from August 26th to September 10th presented 11 days with positive return against 15 days with negative returns. There was no clear sequence on the positive or negative daily mean return.  For instance, from September 2nd to September 4th the daily return were positive, although on September 8 it was negative followed by positive returns for the remaining days.
In the decision-making process, investors can look for past returns of the S&P500 index and use it as a source of information for predicting future outcomes. Although, as studies has shown this kind of prediction can be biased, because streaks of last outcomes do not mean continued success. This assumption is called “Hot hands Fallacy”, a term brought from the belief that basketball players that score more in a game have greater probability of keeping their scores in the next games, which is not true, given the randomness of the event, according to JOSHUA B. MILLER and ADAM SANJURJO in the paper SURPRISED BY THE HOT HAND FALLACY? A TRUTH IN THE LAW OF SMALL NUMBERS: “…the bias can be leveraged to manipulate people into believing that the outcomes of an unpredictable process can be predicted at rates better than chance”.	
When the investor needs to make a quick decision it might be the easiest approach, although it will be rendered to bias and errors in judgment, and may not be give the most accurate information, leading to the wrong investment strategy.	


	
```{r}
save.image("workspace.RData")
```
